A comparative analysis of AquaMaps and IUCN species distribution maps

### 2015-12-18 R/data_explore_am_thresh.Rmd
adding ribbon plot for threshold

### create dataframe that gives me all species, their total number of cells, 
### total number of cells >= 0.4 prob, difference between the two and threat
spp_df3 <- spp_cells %>%
  group_by(species_id) %>%
  summarize(cells_0.4 = sum(probability >= 0.4),
            cells_t = sum(probability >= 0)) %>%
  left_join(spp, by = c('species_id' = 'SPECIESID')) %>%
  mutate(prop = cells_0.4 / cells_t,
         iucn_code = ifelse(is.na(iucn_code), 'NE', iucn_code)) %>%
  filter(toupper(iucn_code) %in% c('LC', 'NT', 'VU', 'EN', 'CR', 'EX', 'DD', 'NE')) %>%
  # filter(toupper(iucn_code) %in% c('LC', 'NT', 'VU', 'EN', 'CR', 'EX')) %>%
  select(sciname, species_id, cells_0.4, cells_t, prop, iucn_code)

@@

ggsave('../figures/AMThreshold.png', width = 6, height = 4)

@@

ggsave('../figures/AMThreshold2.png', width = 6, height = 4)

@@

thresh_df_summary <- threshold_df %>%
  group_by(thresh) %>%
  summarize(mean_prop   = mean(proportion, na.rm = TRUE),
            median_prop = median(proportion, na.rm = TRUE))

@@

ggsave('../figures/scatter_AMThreshold.png', width = 6, height = 4)

@@

>>>>

spp_df3 <- spp_cells %>%
  group_by(species_id) %>%
  summarize(cells_0.4 = sum(probability >= 0.4),
            cells_t = sum(probability >= 0)) %>%
  left_join(spp, by = c('species_id' = 'SPECIESID')) %>%
  mutate(prop = cells_0.4 / cells_t,
         iucn_code = ifelse(is.na(iucn_code), 'NE', iucn_code)) %>%
  filter(toupper(iucn_code) %in% c('LC', 'NT', 'VU', 'EN', 'CR', 'EX', 'DD', 'NE')) %>%
  # filter(toupper(iucn_code) %in% c('LC', 'NT', 'VU', 'EN', 'CR', 'EX')) %>%
  select(sciname, species_id, cells_0.4, cells_t, prop, iucn_code)

@@

ggsave('figures/AMThreshold.png', width = 6, height = 4)

@@

ggsave('figures/AMThreshold2.png', width = 6, height = 4)

@@

thresh_df_summary <- threshold_df %>%
  group_by(thresh) %>%
  summarize(mean_prop   = mean(proportion, na.rm = TRUE),
            median_prop = median(proportion, na.rm = TRUE),
            quant09 = quantile(proportion, .09),
            quant25 = quantile(proportion, .25),
            quant75 = quantile(proportion, .75),
            quant91 = quantile(proportion, .91))

@@

ggsave('figures/scatter_AMThreshold.png', width = 6, height = 4)

@@

```{r boxplot_lost_area_w_threshold, warning = FALSE, message = FALSE, echo = FALSE}

area_mean_model <- lm(mean_prop ~ thresh, data = thresh_df_summary)
area_median_model  <- lm(median_prop ~ thresh,  data = thresh_df_summary)

ribbon_area_vs_threshold <- ggplot(thresh_df_summary, aes(x = thresh, y = median_prop)) + 
  ggtheme_plot + 
#  geom_point(position = position_jitter(w = .1), aes(color = scenario), alpha = .5) +

  geom_ribbon(aes(ymax = quant91, ymin = quant09), alpha = .5, color = NA, fill = 'grey80') +
  geom_ribbon(aes(ymax = quant75, ymin = quant25), alpha = .5, color = NA, fill = 'grey70') +
  geom_point(color = 'grey20') + 
  geom_point(aes(y = mean_prop), color = 'darkred') + 
  geom_abline(intercept = area_mean_model[['coefficients']][1],
              slope     = area_mean_model[['coefficients']][2],
              color = 'red') + 
  geom_vline(x = 0.40, color = 'blue', linetype = 'dashed') +
  geom_vline(x = 0.50, color = 'blue', linetype = 'dashed') +
  geom_vline(x = 0.60, color = 'blue', linetype = 'dashed') +
  annotate('text', x = .40, y = .05, hjust = 0, vjust = -.5,
           angle = 90, size = 2, color = 'grey20',
           label = 'Ocean Health Index: 40%') + 
  annotate('text', x = .50, y = .05, hjust = 0, vjust = -.5,
           angle = 90, size = 2, color = 'grey20',
           label = 'MPA Gap Analysis: 50%') + 
  annotate('text', x = .60, y = .05, hjust = 0, vjust = -.5,
           angle = 90, size = 2, color = 'grey20',
           label = 'Marine mammals: 60%') + 
  annotate('text', x = .75, y = .85,
           size = 2, color = 'grey20',
           label = 'R^2 = .995') + 
  ylim(0, 1) +
  labs(title = 'Relative species range after presence threshold',
       x = 'Presence threshold cutoff', 
       y = 'Mean (median) relative species range')

print(ribbon_area_vs_threshold)

ggsave('figures/ribbon_AMThreshold.png', width = 6, height = 4)
